---
title: "linear model with prediction"
author: "Erika Mondragon"
date: "2023-10-17"
output: html_document
---

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE) 
```


## Model1
find an equation that expresses SIMSA as a function of ARM

## Results

## Graphical Results

```{r}
plot(SIMS~ARM,data=data)
```

As the ARM strength increases, the SIMS score also increases. This is a postive trend between ARM strength and SIMS score trned, not a perfect relationship

## Numerical Results 

```{r}
cor(data$SIMS,data$ARM)
```

We have a positive correlation, with noise. 

## Inference

```{r}
model1 <- lm(SIMS~ARM,data=data)
summary.lm(model1)
```



```{r}
model1 <- lm(SIMS~ARM,data=data)
plot(data$SIMS~data$ARM)
abline(model1, col="red")
```

The red line represents the best linear fit. For an increase of a 1 in ARM strength, SIM score increases by 0.0545. 
